---
title: "InteractionTransformRDemo"
author: "Joshua Levy"
date: "11/18/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## Select python path of conda environment to input in next command
```{r}
reticulate:::conda_list(conda = "auto")
```

## Make sure interaction transformer has been installed into your conda environment
Else, install using the install_transformer command.

## Load package while sourcing python from conda environment
```{r}
library(interactiontransformer)
source.python('/anaconda2/envs/py36/bin/python')
interactiontransformer<-import_transformer()
```


## Loading Test Data

```{r}
df<-read.csv("../test_data/epistasis.test.csv")
X<-df[,-(ncol(df))]
y<-as.data.frame(df[,ncol(df)])
```

## Train test split

```{r}
train.test.splits<-train.test.split(X,y)
```

## Find the top interactions in the training set

```{r}
interaction.transformer<-interaction.fit(train.test.splits$X.train,train.test.splits$y.train,max_train_test_samples = 1000L, mode_interaction_extract = sqrt(ncol(train.test.splits$X.train)))
# reticulate:::py_capture_output()
```
## Transform design matrices for training and test sets

```{r}
X.train2<-interaction.transform(interaction.transformer,train.test.splits$X.train)
X.test2<-interaction.transform(interaction.transformer,train.test.splits$X.test)
```

## Extract top ranked interactions via SHAP

```{r}
interaction.transformer$all_interaction_shap_scores[order(-interaction.transformer$all_interaction_shap_scores[3]),][1:10,]
```

```{r}
sklearn<-reticulate:::import("sklearn")
```

## Fit Models and then get AUROC

```{r}
lr.model<-sklearn$linear_model$LogisticRegression(random_state=42L,class_weight='balanced')$fit(train.test.splits$X.train,train.test.splits$y.train)
lr2.model<-sklearn$linear_model$LogisticRegression(random_state=42L,class_weight='balanced')$fit(X.train2,train.test.splits$y.train)
rf.model<-interactiontransformer$InteractionTransformer$BalancedRandomForestClassifier(random_state=42L)$fit(train.test.splits$X.train,train.test.splits$y.train)

sklearn$metrics$roc_auc_score(train.test.splits$y.test,lr.model$predict_proba(train.test.splits$X.test)[,2])
sklearn$metrics$roc_auc_score(train.test.splits$y.test,lr2.model$predict_proba(X.test2)[,2])
sklearn$metrics$roc_auc_score(train.test.splits$y.test,rf.model$predict_proba(train.test.splits$X.test)[,2])
```

## Collect SHAP Feature Importances

```{r}
shap.results.lr<-run.shap(train.test.splits$X.train, train.test.splits$X.test, lr.model, model_type='linear', savefile='../test_data/epistasis.lr.shap.png')
shap.results.rf<-run.shap(train.test.splits$X.train, train.test.splits$X.test, rf.model, model_type='tree', savefile='../test_data/epistasis.rf.shap.png')
shap.results.lr2<-run.shap(X.train2, X.test2, lr2.model, model_type='linear', savefile='../test_data/epistasis.lr2.shap.png')
```





